A Multi-Modal Model for Prediction and Classification of Object Deformation during Robotic Manipulation

### 2016-08-11 AnswersToComments.tex
Intro to mass-spring added.

\usepackage{color}
\newcommand{\comment}[1]{\textcolor{red}{#1}}

@@

1, in line 37 of page 1, "sensorimotor contingencies" needs to be defined or referenced.

2, in line 35 of page 1, what does "sequencing the models by mode" mean?

3, in line 58 of page 1, the authors claim "In each case the models can be run in two modes, prediction and classification". But the classification mode is not explained later, but a filtering mode is included instead. Besides, please clearly illustrate the mentioned modes and processes in Figure 2.

@@

@@

\comment{Added an introductory paragraph to section IV.}

@@

>>>>

\usepackage{color}
\newcommand{\comment}[1]{\textcolor{blue}{#1}}
\newcommand{\marker}{\hspace*{-1.6em}\textcolor{red}{$\Longrightarrow$}}

@@

\marker
1, in line 37 of page 1, "sensorimotor contingencies" needs to be defined or referenced.

\marker
2, in line 35 of page 1, what does "sequencing the models by mode" mean?

\marker
3, in line 58 of page 1, the authors claim "In each case the models can be run in two modes, prediction and classification". But the classification mode is not explained later, but a filtering mode is included instead. Besides, please clearly illustrate the mentioned modes and processes in Figure 2.

\comment{What does he mean by ``filtering mode instead''?}

@@

\comment{The general idea had been explained in the first paragraph of section IV-A, the details came later.  Since it was not clear enough the wording was modified.}

@@

\comment{Added an introduction at the beginning of section IV.}

@@

\comment{Since for comment 5 the introduction explained that a mass particle is located on vertex i, this has been covered already.}

### 2016-08-11 twostagedo.tex
Intro to mass-spring added.

\comment{This work makes use of the ability of a mass-spring model to predict the shape of a deformable object given its shape at time $t$ and the forces acting on it.  The parameters, that attune this generic model to a particular object, will be obtained through machine learning, and that procedure will be explained in \sref{sec:learning}, since it is independent of the model itself.  Also the forces required as inputs by this mass-spring model will be learned by another module, so that the entire system will require only the initial shape of the object, and the command to be executed, to be able to predict the future behaviour of the object and sensed feedback force.  This section explains the details of the mass-spring model we used.

Mass-spring models are a very well established method to approximately simulate the behaviour of solid deformable objects.  Here, the shape of an object is approximated by a uniform geometric mesh, usually made of triangles (2D) or tetrahedrons (3D).  At every vertex $i$ in the mesh, an ideal particle with no volume, but with mass $m_i$, is located.  The edges between vertices roughly model the interactions between particles that attract each other and at the same time repel each other, therefore maintaining the cohesion of the solid, while avoiding the collapse of the material over itself.  The simplest model associates a linear spring with each edge, as if those forces would occur only between connected neighbours.  The resting state of the solid corresponds to a configuration of the masses and particles where the sum of all forces acting over each particle is zero and they are said to be in equilibrium.

When one or more particles are displaced from their positions of equilibrium, the forces that tend to restore the body to its original shape are modeled by the forces of springs (along the edges of the mesh) that try to recover their original length).  These forces act upon the particles modifying their positions in time.  Traditionally, the relationship between the position of the particle $p_i$ and those forces $F$ obeys the second law of Newton:
\begin{align}
 F = m \dfrac{\partial^2 p}{{\partial t}^2}
\end{align}
where $t$ is time.  However, it is possible to modify this equation according to need if what we are interested in is numerical accuracy, as it will be done here.

Furthermore, the previous equation is a second order differential equation, which is continuous by definition.  In order to obtain a computer simulation from this equation some numerical method will be selected \cite{Nealen2006review}.  Time is discretized in intervals of length $h$, positions and forces at discrete past times are used to estimate the new positions at time $t + h$ according to an integration schemed use to approximately solve the differential equation.  The fact that the value of the forces remain constant for the whole interval $h$ (also know as \textit{time step}), introduces errors which can be severe, depending on their magnitude and the speed at which the force would change during that interval according to the original continuous equation.  For this reason, computer simulations add procedures that pretend to lessen these effects.

Additionally, the mass spring model of the solid object does not specify how the rest of the world interacts with it.  Usually, any external force is introduced as a vector of forces acting on a vertex or as a deformation of the mesh, which breaks the state of equilibrium, thus causing a reaction of the object due to internal forces produced by the springs.  Therefore, to simulate the effects of interacting with the object of interest the model must include the definition of the interactions with surrounding objects (like the effector of the robot).  Those details are shown below.
}

@@

The mass-spring model proposed by Teschner et al.\ in \cite{Teschner2004} was reduced to a 2D model, so that the predictions could be compared with 2D images of the deformable object.  The main idea being that an agent can make rough real time predictions of what it can see and touch and use those predictions to solve various tasks, like classification or grasping.  Here, the surface of the deformable object is approximated by a regular triangular mesh of unitary masses and springs.  The potential energy terms for the preservation of length with damping and preservation of area were included in our system.  To compensate for the lack of a preservation of volume, which tends to avoid distortions of the graph, a new term for the preservation of the angles was included.  The relevant equations are presented in the following paragraphs, while detailed derivations can be found in \cite{Arriola2013thesis}.

For every desired constraint $C(\vec{p}_1,...,\vec{p}_{n})$ acting over $n$ vertices, a potential energy $E$ is defined.  When the value of the constraint is zero, the potential energy is zero as well.  When the constraint is not satisfied, the potential energy increases.  This behaviour is obtained through the following definition for the energy:
\begin{align}
 E(\vec{p}_1,...,\vec{p}_{n}) & = \frac{1}{2}kC(\vec{p}_1,...,\vec{p}_{n})^2, \label{eq:EConstraint}
\end{align}
where $k$ is a proportionality constant \eref{eq:EConstraint} and $p_i$ is the position of particle $i$.

>>>>

\comment{
A mass-spring model is a very well established abstraction used to emulate the behaviour of deformable objects.  As a physics based model, once its parameters are properly assigned, its behaviour is determined by the evolution of a set of differential equations.  Therefore, by offering a method to automatically calibrate those parameters, this model can make long term predictions about the behaviour of deformable objects, under previously unseen interactions, if only the interacting forces are know.  The range of validity of these predictions greatly depends on the quality of the calibration, but also on the suitability of the mass-spring model for the particular object.  For this reason, there are variations that address specific issues, like \cite{Bourguignon2000} and \cite{Teschner2004}.  In this work we focus on the machinery required to achieve this automatic calibration of a physics based model and its integration to a system that exploits it to solve prediction and classification tasks.  We emphasize that the physics based model could be easily substituted by another equivalent model.  For example, the same machine will work if another type of mass-spring model is used, or a FEM model, even though numerical results will differ to some extent.  For these experiments we chose to use a slightly modified version of the mass-spring model proposed by Teschner in \cite{Teschner2004}.

%This work makes use of the ability of a mass-spring model to predict the shape of a deformable object given its shape at time $t$ and the forces acting on it.  The parameters, that attune this generic model to a particular object, will be obtained through machine learning, and that procedure will be explained in \sref{sec:learning}, since it is independent of the model itself.  Also the forces required as inputs by this mass-spring model will be learned by another module, so that the entire system will require only the initial shape of the object, and the command to be executed, to be able to predict the future behaviour of the object and sensed feedback force.  This section explains the details of the mass-spring model we used.

In a simple mass-spring model, the shape of an object is approximated by a uniform geometric mesh, usually made of triangles (2D) or tetrahedrons (3D).  At every vertex $i$ in the mesh, an ideal particle with no volume, but with mass $m_i$, is located.  The edges between vertices roughly model the interactions between particles that attract each other and at the same time repel each other, therefore maintaining the cohesion of the solid, while avoiding the collapse of the material over itself.  The simplest model associates a linear spring with each edge, as if those forces would occur only between connected neighbours.  The resting state of the solid corresponds to a configuration of the masses and particles where the sum of all forces acting over each particle is zero and they are said to be in equilibrium.

When one or more particles are displaced from their positions of equilibrium, the forces that tend to restore an elastic body to its original shape are modeled by the forces of springs (along the edges of the mesh) that try to recover their original length).  These forces act upon the particles modifying their positions in time.  Traditionally, the relationship between the position of the particle $p_i$ and those forces $F$ obeys the second law of Newton:
\begin{align}
 F = m \dfrac{\partial^2 p}{{\partial t}^2} \label{eq:newton}
\end{align}
where $t$ is time.  However, it is possible to modify this equation according to need if what we need is to model a different behaviour. %are interested in is numerical accuracy, as it will be done here.

The previous equation is a second order differential equation, which is continuous by definition.  In order to perform a computer simulation we need to obtain the position $p$ of all vertices as a function of time $p(t)$ using this equation.  A numerical method is selected to approximate a solution \cite{Nealen2006review}.  Time is discretized in intervals of length $h$, positions and forces at discrete past times are used to estimate the new positions at time $t + h$, according to an integration scheme which must be selected.  The fact that the value of the forces remain constant in this approximation, for the whole interval $h$ (also know as \textit{time step}), introduces errors which can be severe.  For this reason, computer simulations may add procedures that help to alleviate these effects.

To simulate the effect of an external actuator (like the finger of the robot) interacting with the deformable object, external forces $F_{ext}$ acting on vertices of the mesh must be added to \eref{eq:newton}:
\begin{align}
 F + F_{ext} = m \dfrac{\partial^2 p}{{\partial t}^2}
\end{align}
Another option could be to induce response forces by displacing vertices from their position of equilibrium.
}

@@

The mass-spring model proposed by Teschner et al.\ in \cite{Teschner2004} was reduced to a 2D model, so that the predictions could be compared with 2D images of the deformable object.  The main idea being that an agent can make rough real time predictions of what it can see and touch and use those predictions to solve various tasks, like classification or grasping.  Here, the surface of the deformable object is approximated by a regular triangular mesh of unitary masses and springs.  The potential energy terms for the preservation of length with damping and preservation of area were included in our system \comment{exactly as they were defined by Teschner}.  To compensate for the lack of a preservation of volume, which tends to avoid distortions of the graph \comment{in the original model}, \comment{we derived } a new term for the preservation of the angles \comment{in every triangle} \sout{was included}.  The relevant equations are presented in the following paragraphs, while detailed derivations can be found in \cite{Arriola2013thesis}.

\comment{Teschner defined a generalized version of the simple mass-spring model by using the concept of \emph{constraint}.  He makes use of different constraints to model the tendency of an object to recover several of its attributes.} For every desired constraint $C(\vec{p}_1,...,\vec{p}_{n})$ acting over $n$ vertices, a potential energy $E$ is defined.  When the value of the constraint is zero, the potential energy is zero as well.  When the constraint is not satisfied, the potential energy increases.  This behaviour is obtained through the following definition for the energy:
\begin{align}
 E(\vec{p}_1,...,\vec{p}_{n}) & = \frac{1}{2}kC(\vec{p}_1,...,\vec{p}_{n})^2, \label{eq:EConstraint}
\end{align}
where $k$ is a proportionality constant \sout{\eref{eq:EConstraint}} and $p_i$ is the position of particle $i$.
